---
title: "Replication Code for Second Deadline"
output: html_document
---

```{r}
rm(list=ls(all=TRUE))
library(foreign)
library(ggplot2)
library(stargazer)
library(arm)
library(rms)
library(msm)
library(systemfit)
library(xtable)
library(gtools)
library(multiwayvcov)
library(numDeriv)
library(interplot)

load("datawork.RData")
```

# Replication of Figure 1 (Chengyu)


# Replication of Table 1 (Frances)

Replicating a function used for decimal places
```{r}
data <- table
head(table)
specify_decimal <- function(x, k) {format(round(x, k), nsmall = k)}
```

These are models creating benchmark OLS estimates for proximity to Soriana stores on vote share:  

```{r}
#regressing different parties on proximity to soriana store 
robustness1 <- ols(proximity ~ PRI06 +PRD06+PAN06+PART06, data= data, x= TRUE, y= TRUE)
```


```{r}
#this is the same as the first but incorporating the municipal districts. i think once we read gary's paper and get a sense of that municipality difference we were talking about 
robustness2 <- ols( proximity ~ PRI06+PRD06+PAN06+PART06+
                      id_mun, data=data, x=TRUE, y=TRUE)
```


```{r}
#this is the larger model
robustness3 <- ols( proximity ~ PRI06+PRD06+PAN06+PART06+
                      lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                      EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                      PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                      PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                      CAR+CELULAR+INTERNET+
                     id_mun, data=data, x=TRUE, y=TRUE)
```


```{r}
robustness4 <- ols( proximity ~ 
                      lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                      EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                      PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                      PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                      CAR+CELULAR+INTERNET+
                      id_mun, data=data, x=TRUE, y=TRUE)
```


This creates a table of covariates

```{r}
stargazer(robustness1, robustness2, robustness3, robustness4, star.cutoffs = c(0.05, 0.01, 0.001), style = "qje", digits=3,
          covariate.labels = c("PRI 2006", "PRD2006", "PAN2006", "Turnout 2006","Population Log", "Population over 18 ",
                               "Population over 65", "Area", "Density", "Indigenous","Catholic","Nonreligious","Education","College degree","Illiteracy","Inhabitants per house","Population in the labor market",
                               "Female population in the labor market", "No insurance","Female head of household","Inhabitants per room", "Dirt floor", "All services", "No services", "Car", "Mobile phone", "Internet", "ACULCO" , "ALMOLOYA DE JUAREZ " , 
                               "ALMOLOYA DEL RIO" , "AMANALCO" , "AMECAMECA" , "APAXCO" , "ATENCO" , "ATIZAPAN" , "ATIZAPAN DE ZARAGOZA" , "AXAPUSCO" , "AYAPANGO" , "CALIMAYA" , "CAPULHUAC" , "CHALCO" , "CHAPULTEPEC" ,
                               "CHIAUTLA" , "CHICOLOAPAN" , "CHICONCUAC" , "CHIMALHUACAN" , "COACALCO DE BERRIOZABAL" , "COCOTITLAN" , "COYOTEPEC" , "CUAUTITLAN" , "CUAUTITLAN IZCALLI" , "ECATEPEC DE MORELOS" , "HUEHUETOCA",
                               "HUEYPOXTLA" , "HUIXQUILUCAN" , "ISIDRO FABELA" , "IXTAPALUCA" , "IXTLAHUACA" , "JALTENCO" , "JILOTEPEC" , "JILOTZINGO" , "JIQUIPILCO" , "JOCOTITLAN" , "JOQUICINGO" , "JUCHITEPEC" , "LA PAZ" ,
                               "LERMA" , "MELCHOR OCAMPO" , "METEPEC" , "MEXICALTZINGO" , "MORELOS" , "NAUCALPAN DE JUAREZ" , "NEXTLALPAN" , "NEZAHUALCOYOTL" , "NICOLAS ROMERO" , "OCOYOACAC" , "OCUILAN" , "OTUMBA" , 
                               "OTZOLOTEPEC" , "PAPALOTLA" , "POLOTITLAN" , "RAYON" , "SAN ANTONIO LA ISLA" , "SAN FELIPE DEL PROGRESO" , "SAN MARTIN DE LAS PIRAMIDES" , "SAN MATEO ATENCO" , "SOYANIQUILPAN DE JUAREZ" , "TECAMAC" ,
                               "TEMAMATLA" , "TEMASCALAPA" , "TEMOAYA" , "TENANGO DEL AIRE" , "TENANGO DEL VALLE" , "TEOLOYUCAN" , "TEOTIHUACAN" , "TEPETLAOXTOC" , "TEPOTZOTLAN" , "TEQUIXQUIAC" , "TEXCALYACAC" , "TEXCOCO" , "TEZOYUCA" ,
                               "TIANGUISTENCO" , "TLALMANALCO" , "TLALNEPANTLA DE BAZ" , "TOLUCA" , "TONANITLA" , "TULTEPEC" , "TULTITLAN" , "VALLE DE CHALCO SOLIDARIDAD" , "VILLA DE ALLEND" , "VILLA DEL CARBON" , "VILLA VICTORIA" , 
                               "XALATLACO" , "XONACATLAN" , "ZINACANTEPEC" , "ZUMPANGO" , "ALVARO OBREGON" , "AZCAPOTZALCO" , "BENITO JUAREZ" , "COYOACAN" , "CUAJIMALPA DE MORELOS" , "CUAUHTEMOC" , "GUSTAVO A. MADERO" , "IZTACALCO" , 
                               "IZTAPALAPA" , "MAGDALENA CONTRERAS" , "MIGUEL HIDALGO" , "MILPA ALTA" , "TLAHUAC" , "TLALPAN" , "VENUSTIANO CARRANZA" , "XOCHIMILCO"))
```

This creates the Benchmark Model table from page 24 of the appendix. 
This is the basis of Table 1. 
```{r}
#reclassifying municipality and district as factor variables
data$id_mun<-factor(data$id_mun)
data$id_dist<-factor(data$id_dist)
```


```{r}
#empty matrices to take the slopes and standard errors of this benchmark model
slopesBM<-matrix(NA,3,4)
seBM<-matrix(NA,3,4)


benchmarkPRI.1 <- lm( EPNa ~ proximity*PRIstr*highTURNOUT+proximity*PRDstr*highTURNOUT+proximity*PANstr*highTURNOUT+     
                         PRI09a+PRD09a+PAN09a+PART09+
                         lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                         EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                         PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                         PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                         CAR+CELULAR+INTERNET+
                         id_mun, data=data, x=TRUE, y=TRUE)
```

This function "returns a multi-way cluster-robust variance-covariance matrix" -- I think this bit right here is related to what Gary was saying on the type of errors and that they can cover up problems with the model. I don't fully understand this right now, but perhaps after we get a little further in the semester. 
```{r}
covBMpri <- cluster.vcov(benchmarkPRI.1, data$id_dist)

#t test
coeftest(benchmarkPRI.1, covBMpri)
```


```{r}
g_pri <- function(b){
  return( b[2] + b[139] + b[140] + b[146] )
}

g_prd <- function(b){
  return( b[2] + b[140] + b[142] + b[147] )
}

g_pan <- function(b){
  return( b[2] + b[140] + b[144] + b[148] )
}

#again, not very sure what this function is doing
grad_g_pri <-  jacobian(g_pri, benchmarkPRI.1$coef)
grad_g_prd <-  jacobian(g_prd, benchmarkPRI.1$coef)
grad_g_pan <-  jacobian(g_pan, benchmarkPRI.1$coef)
```

Taking the slopes and standard errors:
```{r}
slopesBM[1,1] <- benchmarkPRI.1$coefficients[c("proximity")] + benchmarkPRI.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPRI.1$coefficients[c("proximity:PRIstr")]+  benchmarkPRI.1$coefficients[c("proximity:PRIstr:highTURNOUT")]

slopesBM[2,1] <- benchmarkPRI.1$coefficients[c("proximity")] + benchmarkPRI.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPRI.1$coefficients[c("proximity:PRDstr")]+  benchmarkPRI.1$coefficients[c("proximity:highTURNOUT:PRDstr")]

slopesBM[3,1] <- benchmarkPRI.1$coefficients[c("proximity")] + benchmarkPRI.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPRI.1$coefficients[c("proximity:PANstr")]+  benchmarkPRI.1$coefficients[c("proximity:highTURNOUT:PANstr")]

seBM[1,1]<-sqrt(grad_g_pri%*% covBMpri %*% t(grad_g_pri))

seBM[2,1]<-sqrt(grad_g_prd%*% covBMpri %*% t(grad_g_prd))

seBM[3,1]<-sqrt(grad_g_pan%*% covBMpri %*% t(grad_g_pan))
```


The same model for AMLO and the other parties: 
```{r}
benchmarkPRD.1 <- lm( AMLOa ~ proximity*PRIstr*highTURNOUT+proximity*PRDstr*highTURNOUT+proximity*PANstr*highTURNOUT+     
                         PRI09a+PRD09a+PAN09a+PART09+
                         lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                         EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                         PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                         PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                         CAR+CELULAR+INTERNET+
                         id_mun, data=data, x=TRUE, y=TRUE)

covBMprd <- cluster.vcov(benchmarkPRD.1, data$id_dist)

coeftest(benchmarkPRD.1, covBMprd)

g_pri <- function(b){
  return( b[2] + b[139] + b[140] + b[146] )
}

g_prd <- function(b){
  return( b[2] + b[140] + b[142] + b[147] )
}

g_pan <- function(b){
  return( b[2] + b[140] + b[144] + b[148] )
}

grad_g_pri <-  jacobian(g_pri, benchmarkPRD.1$coef)
grad_g_prd <-  jacobian(g_prd, benchmarkPRD.1$coef)
grad_g_pan <-  jacobian(g_pan, benchmarkPRD.1$coef)


slopesBM[1,2] <- benchmarkPRD.1$coefficients[c("proximity")] + benchmarkPRD.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPRD.1$coefficients[c("proximity:PRIstr")]+  benchmarkPRD.1$coefficients[c("proximity:PRIstr:highTURNOUT")]
slopesBM[2,2] <- benchmarkPRD.1$coefficients[c("proximity")] + benchmarkPRD.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPRD.1$coefficients[c("proximity:PRDstr")]+  benchmarkPRD.1$coefficients[c("proximity:highTURNOUT:PRDstr")]
slopesBM[3,2] <- benchmarkPRD.1$coefficients[c("proximity")] + benchmarkPRD.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPRD.1$coefficients[c("proximity:PANstr")]+  benchmarkPRD.1$coefficients[c("proximity:highTURNOUT:PANstr")]
seBM[1,2]<-sqrt(grad_g_pri%*% covBMprd %*% t(grad_g_pri))
seBM[2,2]<-sqrt(grad_g_prd%*% covBMprd %*% t(grad_g_prd))
seBM[3,2]<-sqrt(grad_g_pan%*% covBMprd %*% t(grad_g_pan))


benchmarkPAN.1 <- lm( JVMa ~ proximity*PRIstr*highTURNOUT+proximity*PRDstr*highTURNOUT+proximity*PANstr*highTURNOUT+     
                         PRI09a+PRD09a+PAN09a+PART09+
                         lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                         EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                         PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                         PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                         CAR+CELULAR+INTERNET+
                         id_mun, data=data, x=TRUE, y=TRUE)

covBMpan <- cluster.vcov(benchmarkPAN.1, data$id_dist)

coeftest(benchmarkPAN.1, covBMpan)

g_pri <- function(b){
  return( b[2] + b[139] + b[140] + b[146] )
}

g_prd <- function(b){
  return( b[2] + b[140] + b[142] + b[147] )
}

g_pan <- function(b){
  return( b[2] + b[140] + b[144] + b[148] )
}

grad_g_pri <-  jacobian(g_pri, benchmarkPAN.1$coef)
grad_g_prd <-  jacobian(g_prd, benchmarkPAN.1$coef)
grad_g_pan <-  jacobian(g_pan, benchmarkPAN.1$coef)


slopesBM[1,3] <- benchmarkPAN.1$coefficients[c("proximity")] + benchmarkPAN.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPAN.1$coefficients[c("proximity:PRIstr")]+  benchmarkPAN.1$coefficients[c("proximity:PRIstr:highTURNOUT")]
slopesBM[2,3] <- benchmarkPAN.1$coefficients[c("proximity")] + benchmarkPAN.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPAN.1$coefficients[c("proximity:PRDstr")]+  benchmarkPAN.1$coefficients[c("proximity:highTURNOUT:PRDstr")]
slopesBM[3,3] <- benchmarkPAN.1$coefficients[c("proximity")] + benchmarkPAN.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPAN.1$coefficients[c("proximity:PANstr")]+  benchmarkPAN.1$coefficients[c("proximity:highTURNOUT:PANstr")]
seBM[1,3]<-sqrt(grad_g_pri%*% covBMpan %*% t(grad_g_pri))
seBM[2,3]<-sqrt(grad_g_prd%*% covBMpan %*% t(grad_g_prd))
seBM[3,3]<-sqrt(grad_g_pan%*% covBMpan %*% t(grad_g_pan))


benchmarkPART.1 <- lm( PART ~ proximity*PRIstr*highTURNOUT+proximity*PRDstr*highTURNOUT+proximity*PANstr*highTURNOUT+     
                          PRI09a+PRD09a+PAN09a+PART09+
                          lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                          EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                          PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                          PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                          CAR+CELULAR+INTERNET+
                          id_mun, data=data, x=TRUE, y=TRUE)

covBMpart <- cluster.vcov(benchmarkPART.1, data$id_dist)

coeftest(benchmarkPART.1, covBMpart)

g_pri <- function(b){
  return( b[2] + b[139] + b[140] + b[146] )
}

g_prd <- function(b){
  return( b[2] + b[140] + b[142] + b[147] )
}

g_pan <- function(b){
  return( b[2] + b[140] + b[144] + b[148] )
}

grad_g_pri <-  jacobian(g_pri, benchmarkPART.1$coef)
grad_g_prd <-  jacobian(g_prd, benchmarkPART.1$coef)
grad_g_pan <-  jacobian(g_pan, benchmarkPART.1$coef)

slopesBM[1,4] <- benchmarkPART.1$coefficients[c("proximity")] + benchmarkPART.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPART.1$coefficients[c("proximity:PRIstr")]+  benchmarkPART.1$coefficients[c("proximity:PRIstr:highTURNOUT")]
slopesBM[2,4] <- benchmarkPART.1$coefficients[c("proximity")] + benchmarkPART.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPART.1$coefficients[c("proximity:PRDstr")]+  benchmarkPART.1$coefficients[c("proximity:highTURNOUT:PRDstr")]
slopesBM[3,4] <- benchmarkPART.1$coefficients[c("proximity")] + benchmarkPART.1$coefficients[c("proximity:highTURNOUT")] + benchmarkPART.1$coefficients[c("proximity:PANstr")]+  benchmarkPART.1$coefficients[c("proximity:highTURNOUT:PANstr")]

seBM[1,4]<-sqrt(grad_g_pri%*% covBMpart %*% t(grad_g_pri))
seBM[2,4]<-sqrt(grad_g_prd%*% covBMpart %*% t(grad_g_prd))
seBM[3,4]<-sqrt(grad_g_pan%*% covBMpart %*% t(grad_g_pan))
```

Table 1: 
```{r}
stargazer(coeftest(benchmarkPRI.1, covBMpri), coeftest(benchmarkPRD.1, covBMprd), coeftest(benchmarkPAN.1, covBMpan), coeftest(benchmarkPART.1, covBMpart),style = "qje", star.cutoffs = c(0.05, 0.01, 0.001), digits=3,
          covariate.labels = c("Proximity", "PRI stronghold", "High Mobilization", "PRD stronghold","PAN stronghold", "PRI 2009", "PRD2009", "PAN2009", "Turnout 2009", "Population Log", "Population over 18 ",
                               "Population over 65", "Area", "Density", "Indigenous","Catholic","Nonreligious","Education","College degree","Illiteracy","Inhabitants per house","Population in the labor market",
                               "Female population in the labor market", "No insurance","Female head of household","Inhabitants per room", "Dirt floor", "All services", "No services", "Car", "Mobile phone", "Internet", "ACULCO" , "ALMOLOYA DE JUAREZ " , 
                               "ALMOLOYA DEL RIO" , "AMANALCO" , "AMECAMECA" , "APAXCO" , "ATENCO" , "ATIZAPAN" , "ATIZAPAN DE ZARAGOZA" , "AXAPUSCO" , "AYAPANGO" , "CALIMAYA" , "CAPULHUAC" , "CHALCO" , "CHAPULTEPEC" ,
                               "CHIAUTLA" , "CHICOLOAPAN" , "CHICONCUAC" , "CHIMALHUACAN" , "COACALCO DE BERRIOZABAL" , "COCOTITLAN" , "COYOTEPEC" , "CUAUTITLAN" , "CUAUTITLAN IZCALLI" , "ECATEPEC DE MORELOS" , "HUEHUETOCA",
                               "HUEYPOXTLA" , "HUIXQUILUCAN" , "ISIDRO FABELA" , "IXTAPALUCA" , "IXTLAHUACA" , "JALTENCO" , "JILOTEPEC" , "JILOTZINGO" , "JIQUIPILCO" , "JOCOTITLAN" , "JOQUICINGO" , "JUCHITEPEC" , "LA PAZ" ,
                               "LERMA" , "MELCHOR OCAMPO" , "METEPEC" , "MEXICALTZINGO" , "MORELOS" , "NAUCALPAN DE JUAREZ" , "NEXTLALPAN" , "NEZAHUALCOYOTL" , "NICOLAS ROMERO" , "OCOYOACAC" , "OCUILAN" , "OTUMBA" , 
                               "OTZOLOTEPEC" , "PAPALOTLA" , "POLOTITLAN" , "RAYON" , "SAN ANTONIO LA ISLA" , "SAN FELIPE DEL PROGRESO" , "SAN MARTIN DE LAS PIRAMIDES" , "SAN MATEO ATENCO" , "SOYANIQUILPAN DE JUAREZ" , "TECAMAC" ,
                               "TEMAMATLA" , "TEMASCALAPA" , "TEMOAYA" , "TENANGO DEL AIRE" , "TENANGO DEL VALLE" , "TEOLOYUCAN" , "TEOTIHUACAN" , "TEPETLAOXTOC" , "TEPOTZOTLAN" , "TEQUIXQUIAC" , "TEXCALYACAC" , "TEXCOCO" , "TEZOYUCA" ,
                               "TIANGUISTENCO" , "TLALMANALCO" , "TLALNEPANTLA DE BAZ" , "TOLUCA" , "TONANITLA" , "TULTEPEC" , "TULTITLAN" , "VALLE DE CHALCO SOLIDARIDAD" , "VILLA DE ALLEND" , "VILLA DEL CARBON" , "VILLA VICTORIA" , 
                               "XALATLACO" , "XONACATLAN" , "ZINACANTEPEC" , "ZUMPANGO" , "ALVARO OBREGON" , "AZCAPOTZALCO" , "BENITO JUAREZ" , "COYOACAN" , "CUAJIMALPA DE MORELOS" , "CUAUHTEMOC" , "GUSTAVO A. MADERO" , "IZTACALCO" , 
                               "IZTAPALAPA" , "MAGDALENA CONTRERAS" , "MIGUEL HIDALGO" , "MILPA ALTA" , "TLAHUAC" , "TLALPAN" , "VENUSTIANO CARRANZA" , "XOCHIMILCO"))


```

