---
title: "Distance Visualizations and Model Testing"
output: html_document
---

So, I re-estimated the model using a coarsened categorical variable for the distance. It seems to change the estimates, but I am having trouble generating some play data to make some plots and see (visually) how it changes things due to how complicated this dataset is/all of the factor variables. If any of you feel especially comfortable making up some data, feel free to go for it! 

```{r, results = 'hide', message = FALSE}
library(foreign)
library(stargazer)
library(arm)
library(rms)
library(msm)
library(systemfit)
library(xtable)
library(gtools)
library(multiwayvcov)
library(numDeriv)
library(interplot)
library(modmarg)
library(tidyverse)
library(stats)
library(haven)
library(systemfit)
library(nnet)
library(sjmisc)
library(maptools)
library(rgeos)
library(Imap)
library(spatstat)
```

```{r}
load("datawork.RData")
table <- data
```

```{r}
seq <- quantile(table$distance)
seq <- seq[-5]
seq <- as.numeric(seq)
seq <- c(0, seq, 99.5835360)
table$Distance.Cat <- cut(table$distance, breaks = seq)
```

```{r}
table$Distance.Cat <- as.factor(table$Distance.Cat)
```


Re-estimating the model using the coarsened distance and classical standard errors

```{r}
#reclassifying municipality and district as factor variables
data$id_mun<-factor(data$id_mun)
data$id_dist<-factor(data$id_dist)
```


```{r}
benchmarkPRI.1 <- lm( EPNa ~ Distance.Cat*PRIstr*highTURNOUT+
                        Distance.Cat*PRDstr*highTURNOUT+Distance.Cat*PANstr*highTURNOUT+ 
                         PRI09a+PRD09a+PAN09a+PART09+
                         lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                         EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                         PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                         PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                         CAR+CELULAR+INTERNET+
                         id_mun, data=table, x=TRUE, y=TRUE)


#The same model but testing for other parties: 

benchmarkPRD.1 <- lm( AMLOa ~ Distance.Cat*PRIstr*highTURNOUT+
                        Distance.Cat*PRDstr*highTURNOUT+Distance.Cat*PANstr*highTURNOUT+     
                         PRI09a+PRD09a+PAN09a+PART09+
                         lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                         EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                         PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                         PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                         CAR+CELULAR+INTERNET+
                         id_mun, data=table, x=TRUE, y=TRUE)


benchmarkPAN.1 <- lm( JVMa ~ Distance.Cat*PRIstr*highTURNOUT+Distance.Cat*PRDstr*highTURNOUT+Distance.Cat*PANstr*highTURNOUT+     
                         PRI09a+PRD09a+PAN09a+PART09+
                         lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                         EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                         PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                         PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                         CAR+CELULAR+INTERNET+
                         id_mun, data=table, x=TRUE, y=TRUE)



benchmarkPART.1 <- lm( PART ~ Distance.Cat*PRIstr*highTURNOUT+Distance.Cat*PRDstr*highTURNOUT+Distance.Cat*PANstr*highTURNOUT+     
                          PRI09a+PRD09a+PAN09a+PART09+
                          lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                          EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                          PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                          PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                          CAR+CELULAR+INTERNET+
                          id_mun, data=table, x=TRUE, y=TRUE)

```

```{r}
benchmarkPRI.1.proximity <- lm( EPNa ~ proximity*PRIstr*highTURNOUT+
                        proximity*PRDstr*highTURNOUT+proximity*PANstr*highTURNOUT+ 
                         PRI09a+PRD09a+PAN09a+PART09+
                         lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
                         EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
                         PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
                         PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
                         CAR+CELULAR+INTERNET+
                         id_mun, data=table, x=TRUE, y=TRUE)
```

### Table 1


```{r}
summary(benchmarkPRI.1)
summary(benchmarkPRI.1.proximity)
```

```{r}
####Predicted vote shares in PRD Mobilized Strongholds

g <- glm(EPNa ~ proximity*PRIstr*highTURNOUT+proximity*PRDstr*highTURNOUT+proximity*PANstr*highTURNOUT+     
           PRI09a+PRD09a+PAN09a+PART09+
           lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
           EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
           PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
           PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
           CAR+CELULAR+INTERNET+
           id_mun, data=data, family = 'gaussian')

at.prox <- seq(1/20, 1/2.5, 1/1000)
marg<-marg(mod = g, var_interest = c("proximity"), type = 'levels', data=data[data$PRDstr==1 & data$highTURNOUT==1,],
           at_var_interest = seq(1/20, 1/2.5, 1/1000),  cofint=.95)

#getting confidence intervals for the expected PN turnout in PRD strongholds
mean <- marg[[1]]$Margin
upper <- marg[[1]]$'Lower CI (95%)'
lower <- marg[[1]]$'Upper CI (95%)'

dataPRI<-data.frame(cbind(at.prox, mean, upper, lower))
dataPRI$distance<-(1/dataPRI$at.prox)


#same for AMLO
g <- glm(AMLOa ~ proximity*PRIstr*highTURNOUT+proximity*PRDstr*highTURNOUT+proximity*PANstr*highTURNOUT+     
           PRI09a+PRD09a+PAN09a+PART09+
           lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
           EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
           PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
           PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
           CAR+CELULAR+INTERNET+
           id_mun, data=data, family = 'gaussian')

marg<-marg(mod = g, var_interest = c("proximity"), type = 'levels', data=data[data$PRDstr==1 & data$highTURNOUT==1,],
           at_var_interest = seq(1/20, 1/2.5, 1/1000), cofint=.95)

mean <- marg[[1]]$Margin
upper <- marg[[1]]$'Lower CI (95%)'
lower <- marg[[1]]$'Upper CI (95%)'

dataPRD<-data.frame(cbind(at.prox, mean, upper, lower))
dataPRD$distance<-(1/dataPRD$at.prox)


g <- glm(JVMa ~ proximity*PRIstr*highTURNOUT+proximity*PRDstr*highTURNOUT+proximity*PANstr*highTURNOUT+     
           PRI09a+PRD09a+PAN09a+PART09+
           lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
           EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
           PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
           PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
           CAR+CELULAR+INTERNET+
           id_mun, data=data, family = 'gaussian')

marg<-marg(mod = g, var_interest = c("proximity"), 
           type = 'levels', data=data[data$PRDstr==1 & data$highTURNOUT==1,],
           at_var_interest = seq(1/20, 1/2.5, 1/1000),cofint=.95)

mean <- marg[[1]]$Margin
upper <- marg[[1]]$'Lower CI (95%)'
lower <- marg[[1]]$'Upper CI (95%)'

dataPAN<-data.frame(cbind(at.prox, mean, upper, lower))
dataPAN$distance<-(1/dataPAN$at.prox)

datasim<-data.frame(rbind(dataPRI, dataPRD, dataPAN))

datasim$dv<-NA
datasim$dv[1:351]<-"Peña Nieto"
datasim$dv[352:702]<-"López Obrador"
datasim$dv[703:1053]<-"Vázquez Mota"

ggplot()+
  geom_line(data=datasim, aes(x=distance, y=mean,  linetype=dv))+
  geom_ribbon(data=datasim, aes(x=distance,  ymin=lower, 
                      ymax=upper, fill=dv),  alpha=0.5)+theme_bw()+
  ylab("Predicted vote shares (%)")+
  xlab("Distance to Soriana (km)")+xlim(2.5,20)+ylim(0,50)+ 
  scale_fill_manual(values = c("#F0E442","red", "deepskyblue2"), name="")+
  scale_linetype_manual(values=c("solid", "longdash","dotted"), name="" )+
  theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18),
        legend.text = element_text(size = 18))
```

```{r}
data <- table
```


Trying to re-create this with the coarsened... where I am running into problems...
```{r}
####Predicted vote shares in PRD Mobilized Strongholds

g <- glm(EPNa ~ Distance.Cat*PRIstr*highTURNOUT+Distance.Cat*PRDstr*highTURNOUT+Distance.Cat*PANstr*highTURNOUT+     
           PRI09a+PRD09a+PAN09a+PART09+
           lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
           EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
           PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
           PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
           CAR+CELULAR+INTERNET+
           id_mun, data=table, family = 'gaussian')

Distance.Cat <- seq
marg<-marg(mod = g, var_interest = c("Distance.Cat"), type = 'levels', data=data[data$PRDstr==1 & data$highTURNOUT==1,],  cofint=.95)

#getting confidence intervals for the expected PN turnout in PRD strongholds
mean <- marg[[1]]$Margin
upper <- marg[[1]]$'Lower CI (95%)'
lower <- marg[[1]]$'Upper CI (95%)'

dataPRI<-data.frame(cbind(Distance.Cat, mean, upper, lower))
dataPRI$distance<-(1/dataPRI$Distance.Cat)
```


```{r}
#same for AMLO
g <- glm(AMLOa ~ Distance.Cat*PRIstr*highTURNOUT+Distance.Cat*PRDstr*highTURNOUT+Distance.Cat*PANstr*highTURNOUT+     
           PRI09a+PRD09a+PAN09a+PART09+
           lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
           EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
           PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
           PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
           CAR+CELULAR+INTERNET+
           id_mun, data=table, family = 'gaussian')

marg<-marg(mod = g, var_interest = c("Distance.Cat"), type = 'levels', data=data[data$PRDstr==1 & data$highTURNOUT==1,],
           at_var_interest = seq(1/20, 1/2.5, 1/1000), cofint=.95)

mean <- marg[[1]]$Margin
upper <- marg[[1]]$'Lower CI (95%)'
lower <- marg[[1]]$'Upper CI (95%)'

dataPRD<-data.frame(cbind(at.prox, mean, upper, lower))
dataPRD$distance<-(1/dataPRD$at.prox)


g <- glm(JVMa ~ Distance.Cat*PRIstr*highTURNOUT+Distance.Cat*PRDstr*highTURNOUT+Distance.Cat*PANstr*highTURNOUT+     
           PRI09a+PRD09a+PAN09a+PART09+
           lnpop+P18+P65+area+density+INDIGENOUS+CATHOLIC+NONRELIGIOUS+
           EDUCATION+POSTEDUC+ILLITERACY+PROM_HNV+
           PEAprop+PEAfemale+NOINSURANCE+FEMALEJEFA+
           PERROOM+DIRTFLOOR+SERVICES+NO_SERVICES+
           CAR+CELULAR+INTERNET+
           id_mun, data=data, family = 'gaussian')

marg<-marg(mod = g, var_interest = c("proximity"), 
           type = 'levels', data=data[data$PRDstr==1 & data$highTURNOUT==1,],
           at_var_interest = seq(1/20, 1/2.5, 1/1000),cofint=.95)

mean <- marg[[1]]$Margin
upper <- marg[[1]]$'Lower CI (95%)'
lower <- marg[[1]]$'Upper CI (95%)'

dataPAN<-data.frame(cbind(at.prox, mean, upper, lower))
dataPAN$distance<-(1/dataPAN$at.prox)

datasim<-data.frame(rbind(dataPRI, dataPRD, dataPAN))

datasim$dv<-NA
datasim$dv[1:351]<-"Peña Nieto"
datasim$dv[352:702]<-"López Obrador"
datasim$dv[703:1053]<-"Vázquez Mota"

ggplot()+
  geom_line(data=datasim, aes(x=distance, y=mean,  linetype=dv))+
  geom_ribbon(data=datasim, aes(x=distance,  ymin=lower, 
                      ymax=upper, fill=dv),  alpha=0.5)+theme_bw()+
  ylab("Predicted vote shares (%)")+
  xlab("Distance to Soriana (km)")+xlim(2.5,20)+ylim(0,50)+ 
  scale_fill_manual(values = c("#F0E442","red", "deepskyblue2"), name="")+
  scale_linetype_manual(values=c("solid", "longdash","dotted"), name="" )+
  theme(axis.text=element_text(size=18),
        axis.title=element_text(size=18),
        legend.text = element_text(size = 18))
```





The general plots from friday:
```{r}
plot(EPNa ~ distance, data = table)

plot(EPNa ~ proximity, data = table)
```


```{r}
plot(EPNa ~ Distance.Cat, xlim = c(0, 40), data = table)
```

